% Code

```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

# FLS Data


```{r}
library(tidyverse)
library(metafor)
library(janitor)
library(here)
library(cowplot)
fls_sev <- read_csv("data/dat-sev.csv")
fls_sev

```


## Active ingredients

```{r}

library(metafor)


mv_sev_HCS <- rma.mv(log_sev, vi_sev,
  mods = ~active_ingred,
  random = list(~active_ingred | factor(study)),
  struct = "HCS",
  method = "ML",
  data = fls_sev
)


mv_sev_HCS
```




### Percent control


```{r}

efficacy_sev <- data.frame(cbind(
  (1 - exp(mv_sev_HCS$b)) * 100,
  (1 - exp(mv_sev_HCS$ci.lb)) * 100,
  (1 - exp(mv_sev_HCS$ci.ub)) * 100))

efficacy_sev

```

```{r}

efficacy_res = efficacy_sev %>% 
  set_names("efficacy", "efficacy_up", "efficacy_lw") %>% 
  mutate(fungicide = c("check", "AZOX + DIFE", "DIFE + PYDI", "PYRA", "PYRA + FLUX + PROP", "TFLX + PROT","TMET", "TMET + TEBU", "TTRA")) %>% 
  filter(fungicide != "check")
efficacy_res

library(readr)
write_csv(efficacy_res, "data/efficacy.csv")
```


### Contrasts

We can set linear contrasts between treatments of interest and get the P-value using the `anova` function.


```{r}
anova(mv_sev_HCS, L = rbind(
  c(0, 1, -1, 0, 0, 0, 0, 0, 0),
  c(0, 1, 0, -1, 0, 0, 0, 0, 0),
  c(0, 1, 0, 0, -1, 0, 0, 0, 0),
  c(0, 1, 0, 0, 0, -1, 0, 0, 0),
  c(0, 1, 0, 0, 0, 0, -1, 0, 0),
  c(0, 1, 0, 0, 0, 0, 0, -1, 0),
  c(0, 1, 0, 0, 0, 0, 0, 0, -1),
  c(0, 0, 1, -1, 0, 0, 0, 0, 0),
  c(0, 0, 1, 0, -1, 0, 0, 0, 0),
  c(0, 0, 1, 0, 0, -1, 0, 0, 0),
  c(0, 0, 1, 0, 0, 0, -1, 0, 0),
  c(0, 0, 1, 0, 0, 0, 0, -1, 0),
  c(0, 0, 1, 0, 0, 0, 0, 0, -1),
  c(0, 0, 0, 1, -1, 0, 0, 0, 0),
  c(0, 0, 0, 1, 0, -1, 0, 0, 0),
  c(0, 0, 0, 1, 0, 0, -1, 0, 0),
  c(0, 0, 0, 1, 0, 0, 0, -1, 0),
  c(0, 0, 0, 1, 0, 0, 0, 0, -1),
  c(0, 0, 0, 0, 1, -1, 0, 0, 0),
  c(0, 0, 0, 0, 1, 0, -1, 0, 0),
  c(0, 0, 0, 0, 1, 0, 0, -1, 0),
  c(0, 0, 0, 0, 1, 0, 0, 0, -1),
  c(0, 0, 0, 0, 0, 1, -1, 0, 0),
  c(0, 0, 0, 0, 0, 1, 0, -1, 0),
  c(0, 0, 0, 0, 0, 1, 0, 0, -1),
  c(0, 0, 0, 0, 0, 0, 1, -1, 0),
  c(0, 0, 0, 0, 0, 0, 1, 0, -1),
  c(0, 0, 0, 0, 0, 0, 0, 1, -1)))
```



## Mod: YEAR

```{r}
library(metafor)
summary(fls_sev$vi_sev)
fls_sev1 <- fls_sev %>%
  filter(mean_sev > 0) %>% 
  filter(vi_sev > 0.001) %>% 
  filter(year  %in% c(2015,2016,2017,2018,2019,2020)) %>% 
  filter(active_ingred %in% c("AACHECK","AZOX + DIFE", "PYRA", "TMET", "TMET + TEBU", "TTRA", "PYRA + FLUX + PROP"))
  


mv_sev_year <- rma.mv(log_sev, vi_sev,
   mods = ~active_ingred*year,
   random = list(~active_ingred | factor(study)),
   struct = "HCS",
   method = "ML",
  #control = list(optimizer = "nlm"),
   data = fls_sev1  %>% mutate(year= year - 2015))


 mv_sev_year

anova(mv_sev_year, btt = 9:14)
```

## Decline efficacy 

```{r fig.height=8, fig.width=10}
library(here)

fls_effic <- fls_sev %>%
 # filter(state  %in% c("Alabama", "Arkansas", "Kentucky", "Louisiana", "Iowa")) %>%
  filter(year  %in% c(2015,2016,2017,2018,2019,2020)) %>%
  filter(active_ingred %in% c("AACHECK","AZOX + DIFE", "PYRA", "TMET", "TMET + TEBU", "TTRA", "PYRA + FLUX + PROP")) %>%
  mutate(efficacy = (1-(mean_sev/sev_check))) %>%
  mutate(efficacy1 = efficacy*100) %>%
  filter(active_ingred!= "AACHECK")
  


reg1 = data.frame(mv_sev_year$beta, mv_sev_year$ci.lb, mv_sev_year$ci.ub) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado1, into = c("lixo", "lado3"),sep = "active_ingred") %>%
  select(-lixo) %>%
  filter(lado3 != "NA") %>%
  set_names("fungicide", "mod", "mean", "ci.lb", "ci.ub") %>%
  mutate(mod = c(rep("intercept", 6), rep("slope", 6))) %>%  
  filter(fungicide %in% c("AZOX + DIFE", "PYRA", "TMET", "TMET + TEBU", "TTRA", "PYRA + FLUX + PROP"))
  # filter(fungicide %in% c("AZOX + DIFE", "PYRA", "TMET", "TMET + TEBU", "TTRA", "FLUO + FLUT")) 

  

reg2 = reg1 %>%
  group_by(fungicide) %>%
  select(1:3) %>%
  spread(mod, mean) %>% 
  set_names("fungicide", "intercept_mean", "slope_mean")

upper = reg1 %>%
  group_by(fungicide) %>%
  select(1:2,4) %>%
  spread(mod, ci.lb) %>% 
  set_names("fungicide", "intercept_upper", "slope_upper")

lower = reg1 %>%
  group_by(fungicide) %>%
  select(1:2,5) %>%
  spread(mod, ci.ub) %>% 
  set_names("fungicide", "intercept_lower", "slope_lower")

data_model = left_join(reg2, lower, by= c("fungicide")) %>% 
  left_join(upper, by = c("fungicide"))


year = seq(0,4, by = 0.1) 
fungicide = NULL
year_col = NULL
for(i in 1:length(data_model$fungicide)){
data_cache = fls_effic %>% 
    filter(active_ingred == data_model$fungicide[i]) 
years = unique(data_cache$year)-2015
year = seq(first(years),last(years), by = 0.1)   
  year_col = c(year_col,year) 
  fungicide = c(fungicide, rep(data_model$fungicide[i], length(year)))
}
 
predicted = data.frame(year_col, fungicide) %>%
  mutate(year = year_col) %>% 
  right_join(data_model, by = "fungicide") %>% 
  # filter(fungicide %in% c("AZOX + DIFE", "PYRA", "TMET", "TMET + TEBU", "TTRA", "FLUO + FLUT")) %>%
  #filter(fungicide %in% c("PYRA", "TMET", "TTRA")) %>% 
  mutate(mean_efficacy = (1-exp(intercept_mean + slope_mean*year))*100,
         CIL = (1-exp(intercept_lower + slope_lower*year))*100,
         CIU = (1-exp(intercept_upper + slope_upper*year))*100,
         year = year+2015) %>% 
  mutate(active_ingred = fungicide) %>% 
  dplyr::select(-fungicide)

```

```{r fig.height=10, fig.width=8}
library(ggthemes)
# fls_effic1 = fls_effic %>% 
#   filter(active_ingred %in% c("PYRA", "TMET", "TTRA")) %>%
#   mutate(active_ingred = case_when(
#     active_ingred == "PYRA" ~ "Pyraclostrobin",
#     active_ingred == "TTRA" ~ "Tetraconazole",
#     active_ingred == "TMET" ~ "Thiophanate-methyl")) 

  ggplot()+
  geom_jitter(data = fls_effic, aes(year, efficacy1, size = vi_sev, color = state), alpha= 0.6, width = .15)+
  geom_line(data = predicted, aes(year, mean_efficacy), size = 1, color = "steelblue")+
  geom_line(data = predicted, aes(year, CIL), linetype="dashed", size = 1, alpha = 0.6)+
  geom_line(data = predicted, aes(year, CIU), linetype="dashed", size = 1, alpha = 0.6)+
  theme_minimal_grid()+
  scale_color_calc()+
  ylim(0,100)+
  theme(legend.position = "right",
        legend.title.align = 0.5,
        legend.title = element_text(size = 12, face = "bold"),
        legend.text = element_text(size = 12),
        axis.text.x = element_text(size = 10, angle = 60, hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size=14, face = "bold"),
        axis.title.y = element_text(size=14, face = "bold"),
        strip.text = element_text(size = 12, face = "bold", color = "white"),
        strip.background = element_rect(colour="black", fill="black"))+
  labs(y = "Efficacy (%)", x = "Years", size = "Sampling Variance", color = "State")+
  facet_wrap(~active_ingred, ncol = 2)
ggsave("Figures/decline_efficacy.png", width = 8, height = 6,bg = "white", dpi = 600)
```

## Mod: yield_class

```{r}
#Moderator yield_class

summary(fls_sev$yld_check) # Median = 3200; Mean = 3039 

fls_sev <- fls_sev %>%
  mutate(yld_check_class = case_when(
      yld_check < 3200 ~ "low",
      yld_check >= 3200 ~ "high"))
table(fls_sev$active_ingred, fls_sev$yld_check_class)


mv_yld_check <- rma.mv(log_sev, vi_sev,
  mods = ~active_ingred * factor(yld_check_class),
  random = list(~active_ingred | factor(study)),
  struct = "HCS",
  method = "ML",
  #control = list(optimizer = "nlm"),
  data = fls_sev
)


mv_yld_check


anova(mv_yld_check, btt=11:18)


```

## Mod:Baseline

```{r}
library(tidyverse)

summary(fls_sev$sev_check) 

fls_sev <- fls_sev %>%
  mutate(
    sev_check_class = case_when(
      sev_check < 14 ~ "Low",
      sev_check >= 14 ~ "High"))

mv_sev_bas <- rma.mv(log_sev, vi_sev,
  mods = ~active_ingred * as.factor(sev_check_class),
  random = list(~active_ingred | factor(study)),
  struct = "HCS",
  method = "ML",
  data = fls_sev
)


mv_sev_bas

anova(mv_sev_bas, btt = 11:18)
```

### Design groups

```{r}
fls_sev1 = fls_sev %>% 
  group_by(study) %>% 
  summarise(active_ingred1 = paste(active_ingred, collapse=';')) 

fls_sev1 %>% 
  tabyl(active_ingred1)
```


Sixteen different designs (here design refers to the set of treatments in the trial) were found in the trials reporting FLS severity.

```{r}
fls_sev <- fls_sev %>%
  group_by(study) %>% 
  mutate(n2 = n()) %>% 
  filter(n2 != 1)

design1 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "PYRA + FLUX + PROP", "DIFE + PYDI", "TMET + TEBU", "PYRA")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(1, length(active_ingred))) %>% 
  filter(n2 == 5) %>% 
  filter(n3 == 5)
design1

design2 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "PYRA + FLUX + PROP", "DIFE + PYDI", "TMET + TEBU", "PYRA", "AZOX + DIFE")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(2, length(active_ingred))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design2

design3 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TMET", "PYRA")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(3, length(active_ingred))) %>% 
  filter(n2 == 3) %>% 
  filter(n3 == 3)
design3

design4 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TMET", "PYRA", "AZOX + DIFE")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(4, length(active_ingred))) %>% 
  filter(n2 == 4) %>% 
  filter(n3 == 4)
design4

design5 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TMET", "TMET + TEBU", "PYRA", "AZOX + DIFE", "TFLX + PROT")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(5, length(active_ingred))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design5

design6 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "DIFE + PYDI", "TMET", "PYRA", "AZOX + DIFE")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(6, length(active_ingred))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design6

design7 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "PYRA + FLUX + PROP", "DIFE + PYDI", "TMET", "PYRA")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(7, length(active_ingred))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design7

design8 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "PYRA + FLUX + PROP", "DIFE + PYDI", "TMET", "TMET + TEBU", "PYRA", "AZOX + DIFE")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(8, length(active_ingred))) %>% 
  filter(n2 == 8) %>% 
  filter(n3 == 8)
design8

design9 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "PYRA + FLUX + PROP", "TMET + TEBU", "PYRA", "AZOX + DIFE", "TFLX + PROT")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(9, length(active_ingred))) %>% 
  filter(n2 == 7) %>% 
  filter(n3 == 7)
design9

design10 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "PYRA + FLUX + PROP", "TMET", "TMET + TEBU", "PYRA", "AZOX + DIFE")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(10, length(active_ingred))) %>% 
  filter(n2 == 7) %>% 
  filter(n3 == 7)
design10

design11 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "PYRA + FLUX + PROP", "TMET", "TMET + TEBU", "PYRA", "AZOX + DIFE", "TFLX + PROT")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(11, length(active_ingred))) %>% 
  filter(n2 == 8) %>% 
  filter(n3 == 8)
design11

design12 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "TMET + TEBU", "PYRA")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(12, length(active_ingred))) %>% 
  filter(n2 == 4) %>% 
  filter(n3 == 4)
design12

design13 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "TMET", "PYRA", "AZOX + DIFE")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(13, length(active_ingred))) %>% 
  filter(n2 == 5) %>% 
  filter(n3 == 5)
design13

design14 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "TMET", "TMET + TEBU", "AZOX + DIFE", "TFLX + PROT")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(14, length(active_ingred))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design14

design15 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "TMET", "TMET + TEBU", "PYRA", "AZOX + DIFE")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(15, length(active_ingred))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design15

design16 = fls_sev %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "TMET", "TMET + TEBU", "PYRA", "AZOX + DIFE", "TFLX + PROT")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(16, length(active_ingred))) %>% 
  filter(n2 == 7) %>% 
  filter(n3 == 7)
design16

sev_design = rbind(design1, design2, design3, design4, design5, design6, design7, design8, design9, design10, design11, design12, design13, design14, design15, design16)


sev_design %>% 
  group_by(study,design) %>% 
  summarize() %>% 
  tabyl(design)
```

### Inconsistency

```{r}
mv_sev_design <- rma.mv(log_sev, vi_sev,
  mods = ~active_ingred * design,
  random = list(~ 1 | study / design / active_ingred),
  struct = "HCS",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = sev_design)

mv_sev_design

anova(mv_sev_design, btt = 11:18)

```






