% Code



## Data

```{r, warning=FALSE}
library(tidyverse)
library(metafor)
library(janitor)
fls_yld <- read_csv("data/dat-yld.csv")
fls_yld
```


## Active Ingredientes

### Absolute yld 

```{r}

library(metafor)

mv_yld <- rma.mv(mean_yld, vi_yld,
  mods = ~active_ingred,
  random = list(~active_ingred | study),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fls_yld
)

summary(mv_yld)
```


```{r}
yield_res<- data.frame(cbind(mv_yld$b, 
                             mv_yld$ci.lb,
                             mv_yld$ci.ub)) %>% 
  set_names("yld", "yld_lw", "yld_upp") %>% 
  mutate(fungicide = c("check", "AZOX + DIFE", "DIFE + PYDI", "PYRA", "PYRA + FLUX + PROP", "TFLX + PROT","TMET", "TMET + TEBU", "TTRA")) %>% 
  filter(fungicide != "check")
yield_res

library(tidyverse)
efficacy_res <- read_csv("data/efficacy.csv")


sev_yld = full_join(efficacy_res, yield_res)
sev_yld

library(readr)
write_csv(sev_yld, "data/sev_yld.csv")
```




### Contrasts

We can set linear contrasts between treatments of interest and get the P-value using the `anova` function.


```{r}
anova(mv_yld, L = rbind(
  c(0, 1, -1, 0, 0, 0, 0, 0, 0),
  c(0, 1, 0, -1, 0, 0, 0, 0, 0),
  c(0, 1, 0, 0, -1, 0, 0, 0, 0),
  c(0, 1, 0, 0, 0, -1, 0, 0, 0),
  c(0, 1, 0, 0, 0, 0, -1, 0, 0),
  c(0, 1, 0, 0, 0, 0, 0, -1, 0),
  c(0, 1, 0, 0, 0, 0, 0, 0, -1),
  c(0, 0, 1, -1, 0, 0, 0, 0, 0),
  c(0, 0, 1, 0, -1, 0, 0, 0, 0),
  c(0, 0, 1, 0, 0, -1, 0, 0, 0),
  c(0, 0, 1, 0, 0, 0, -1, 0, 0),
  c(0, 0, 1, 0, 0, 0, 0, -1, 0),
  c(0, 0, 1, 0, 0, 0, 0, 0, -1),
  c(0, 0, 0, 1, -1, 0, 0, 0, 0),
  c(0, 0, 0, 1, 0, -1, 0, 0, 0),
  c(0, 0, 0, 1, 0, 0, -1, 0, 0),
  c(0, 0, 0, 1, 0, 0, 0, -1, 0),
  c(0, 0, 0, 1, 0, 0, 0, 0, -1),
  c(0, 0, 0, 0, 1, -1, 0, 0, 0),
  c(0, 0, 0, 0, 1, 0, -1, 0, 0),
  c(0, 0, 0, 0, 1, 0, 0, -1, 0),
  c(0, 0, 0, 0, 1, 0, 0, 0, -1),
  c(0, 0, 0, 0, 0, 1, -1, 0, 0),
  c(0, 0, 0, 0, 0, 1, 0, -1, 0),
  c(0, 0, 0, 0, 0, 1, 0, 0, -1),
  c(0, 0, 0, 0, 0, 0, 1, -1, 0),
  c(0, 0, 0, 0, 0, 0, 1, 0, -1),
  c(0, 0, 0, 0, 0, 0, 0, 1, -1)))
```

### Year as continuous

```{r}

library(metafor)

fls_yld1 <- fls_yld %>%
  filter(vi_yld > 1) %>% 
   filter(year  %in% c(2015,2016,2017,2018,2019,2020)) %>% 
    filter(active_ingred %in% c("AACHECK", "AZOX + DIFE", "PYRA", "TMET", "TMET + TEBU", "TTRA", "PYRA + FLUX + PROP")) 


mv_yld_year <- rma.mv(mean_yld, vi_yld,
   mods = ~active_ingred*year,
   random = list(~active_ingred | factor(study)),
   struct = "UN",
   method = "ML",
   control = list(optimizer = "nlm"),
   data = fls_yld1 %>% mutate(year= year - 2015))

 mv_yld_year


anova(mv_yld_year, btt = 9:14)
```



### Disease Pressure


```{r}


library(tidyverse)

summary(fls_yld$sev_check) 

fls_yld <- fls_yld %>%
  mutate(
    sev_check_class = case_when(
      sev_check < 14 ~ "Low",
      sev_check >= 14 ~ "High"))

library(janitor) 
fls_yld %>%
  tabyl(active_ingred, sev_check_class)

mv_yld_bas <- rma.mv(mean_yld, vi_yld,
  mods = ~active_ingred * as.factor(sev_check_class),
  random = list(~active_ingred | factor(study)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fls_yld)


mv_yld_bas

anova(mv_yld_bas, btt = 11:18)
```


#### Mod effect

```{r}
library(here)
reg1 = data.frame(mv_yld_bas$beta, mv_yld_bas$ci.lb, mv_yld_bas$ci.ub) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado2, into = c("lixo","lado3"),sep = "sev_check_class") %>% 
  select(-lixo) %>%
  separate(lado1, into = c("lixo","lado1"),sep = "active_ingred" ) %>%
  select(-lixo) %>%
  filter(lado1 != "NA") %>%
  mutate(n = seq(1:16))
names(reg1) = c("fungicide", "class", "mean", "ci.lb", "ci.ub", "n") 

reg2 = reg1 %>%
  filter(n < 9) %>% 
  mutate(class = rep("High", length(fungicide)))

reg3 = reg1 %>% 
  filter(n > 8) %>% 
  mutate(class = rep("Low", length(fungicide)))

reg4 = rbind(reg2,reg3)  

mean = reg4%>% 
  group_by(fungicide) %>% 
  select(1:3) %>% 
  spread(class, mean) %>% 
  mutate(mean = High + Low) %>% 
  select(1,4)

lower = reg4%>% 
  group_by(fungicide) %>% 
  select(1,2,4) %>% 
  spread(class, ci.lb) %>% 
  mutate(lower = High + Low) %>%  
  select(1,4)

upper = reg4%>% 
  group_by(fungicide) %>% 
  select(1,2,5) %>% 
  spread(class, ci.ub) %>% 
  mutate(upper = High + Low) %>% 
  select(1,4)

reg5 = left_join(mean, lower, by= c("fungicide")) %>% 
  left_join(upper, by = c("fungicide")) %>% 
  mutate(class = rep("Low", length("fungicide"))) %>% 
  select("fungicide", "class", "mean", "lower", "upper")


High = reg4 %>% 
  filter(class == "High") %>% 
  select(1:5)
names(High) = c("fungicide", "class", "mean", "lower", "upper") 

reg6 = full_join(High,reg5)
reg6

openxlsx::write.xlsx(reg6, here("data","yld_baseline.xlsx"), colNames = TRUE)
```

### Design groups

```{r}
fls_yld1 = fls_yld %>% 
  filter(year != 2011) %>% 
  group_by(study) %>% 
  summarise(active_ingred1 = paste(active_ingred, collapse=';')) 

fls_yld1 %>% 
  tabyl(active_ingred1)
```

Nineteen different designs (here design refers to the set of treatments in the trial) were found in the trials reporting soybean yield.

```{r}
fls_yld <- fls_yld %>%
  group_by(study) %>% 
  mutate(n2 = n()) %>% 
  filter(n2 != 1)

design1 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "AZOX + DIFE")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(1, length(active_ingred))) %>% 
  filter(n2 == 2) %>% 
  filter(n3 == 2)
design1

design2 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "DIFE + PYDI")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(2, length(active_ingred))) %>% 
  filter(n2 == 2) %>% 
  filter(n3 == 2)
design2

design3 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "PYRA + FLUX + PROP", "DIFE + PYDI", "TMET + TEBU","PYRA")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(3, length(active_ingred))) %>% 
  filter(n2 == 5) %>% 
  filter(n3 == 5)
design3

design4 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TMET", "PYRA", "AZOX + DIFE")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(4, length(active_ingred))) %>% 
  filter(n2 == 4) %>% 
  filter(n3 == 4)
design4

design5 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TMET", "TMET + TEBU", "PYRA", "AZOX + DIFE", "TFLX + PROT")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(5, length(active_ingred))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design5

design6 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "DIFE + PYDI", "TMET", "PYRA", "AZOX + DIFE")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(6, length(active_ingred))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design6

design7 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "PYRA + FLUX + PROP", "DIFE + PYDI", "TMET", "PYRA")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(7, length(active_ingred))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design7

design8 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "PYRA + FLUX + PROP", "DIFE + PYDI", "TMET", "TMET + TEBU", "PYRA", "AZOX + DIFE")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(8, length(active_ingred))) %>% 
  filter(n2 == 8) %>% 
  filter(n3 == 8)
design8

design9 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "PYRA + FLUX + PROP", "TMET + TEBU", "PYRA", "AZOX + DIFE", "TFLX + PROT")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(9, length(active_ingred))) %>% 
  filter(n2 == 7) %>% 
  filter(n3 == 7)
design9

design10 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "PYRA + FLUX + PROP", "TMET", "TMET + TEBU", "PYRA", "AZOX + DIFE")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(10, length(active_ingred))) %>% 
  filter(n2 == 7) %>% 
  filter(n3 == 7)
design10

design11 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "PYRA + FLUX + PROP", "TMET", "TMET + TEBU", "PYRA", "AZOX + DIFE", "TFLX + PROT")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(11, length(active_ingred))) %>% 
  filter(n2 == 8) %>% 
  filter(n3 == 8)
design11

design12 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "TMET + TEBU", "PYRA")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(12, length(active_ingred))) %>% 
  filter(n2 == 4) %>% 
  filter(n3 == 4)
design12

design13 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK",  "TMET", "PYRA")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(13, length(active_ingred))) %>% 
  filter(n2 == 3) %>% 
  filter(n3 == 3)
design13

design14 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "TMET", "TMET + TEBU", "AZOX + DIFE", "TFLX + PROT")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(14, length(active_ingred))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design14

design15 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "TMET", "TMET + TEBU", "PYRA", "AZOX + DIFE")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(15, length(active_ingred))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design15

design16 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "TMET", "TMET + TEBU", "PYRA", "AZOX + DIFE", "TFLX + PROT")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(16, length(active_ingred))) %>% 
  filter(n2 == 7) %>% 
  filter(n3 == 7)
design16

design17 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "PYRA + FLUX + PROP", "DIFE + PYDI", "TMET + TEBU", "PYRA")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(17, length(active_ingred))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design17

design18 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "PYRA + FLUX + PROP", "DIFE + PYDI", "TMET", "PYRA", "AZOX + DIFE")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(18, length(active_ingred))) %>% 
  filter(n2 == 7) %>% 
  filter(n3 == 7)
design18

design19 = fls_yld %>% 
  group_by(study) %>% 
  filter(active_ingred  %in% c("AACHECK", "TTRA", "PYRA + FLUX + PROP", "DIFE + PYDI", "TMET", "TMET + TEBU", "PYRA")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(19, length(active_ingred))) %>% 
  filter(n2 == 7) %>% 
  filter(n3 == 7)
design19

yld_design = rbind(design1, design2, design3, design4, design5, design6, design7, design8, design9, design10, design11, design12, design13, design14, design15, design16, design17, design18, design19)


yld_design %>% 
  group_by(study,design) %>% 
  summarize() %>% 
  tabyl(design)
```


### Inconsistency

```{r}
mv_yld_design <- rma.mv(mean_yld, vi_yld,
  mods = ~active_ingred * design,
  random = list(~ 1 | study / design / active_ingred),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = yld_design)

mv_yld_design

anova(mv_yld_design, btt = 11:18)

```





